---
runtime: shiny
output: html_document
---

```{r echo = FALSE}
binner <- function(var) {
  require(shiny)
  shinyApp(
    ui = fluidPage(
      sidebarLayout(
        sidebarPanel(sliderInput("n", "Bins", 5, 100, 20)),
        mainPanel(plotOutput("hist"))
      )
    ), 
    server = function(input, output) {
      output$hist <- renderPlot( 
        hist(var, breaks = input$n,
          col = "skyblue", border = "white") 
      )
    }
  )
}
```

## Old Faithful

Old faithful tends to erupt at regular intervals (hence its name). But how regular are these intervals?  

I went to Yellowstone national park and monitored the old faithful geyser during fourteen days. During this time I wrote down the exact number of minutes that passed between each eruption.

Just kidding, I used the `faithful` data set which comes with R. It contains the same information. Below is a histogram of the results. As you can see the times are bimodal. Old faithful is not entirely faithful; it appears to have a mistress on the side.

```{r echo = FALSE}
binner(faithful$waiting)
```