---
title: "Weekly Roto"
output: 
  html_document:
    toc: false
---

```{r, echo=FALSE,message=FALSE,warning=FALSE}
library(tidyverse)
library(DT)
library(knitr)
library(kableExtra)
library(htmlTable)

##Code Necessary for Weekly ROTO winners



all_week_stats <- read_delim("/Users/noahknoblauch/Baseball/all_week_stats.txt",delim = "\t",guess_max = 10000)

all_week_stats <- all_week_stats %>%
  filter(Stat != "Hits / At Bats", Stat != "IP") %>%
  mutate(stat_value = as.numeric(stat_value)) %>%
  group_by(Stat,week) %>%
  mutate(roto_points = ifelse(Stat == "WHIP" | Stat == "ERA",rank(-stat_value),rank(stat_value)))

Scoreboard <- all_week_stats %>% group_by(real_name,week) %>% summarise(total = sum(roto_points))

Scoreboard <- arrange(Scoreboard,week)
winners <- Scoreboard %>% group_by(week) %>% filter(total == max(total)) %>% filter(week != 22,week != 23,week != 24)
winners <- rename(winners,Manager = real_name,Week = week,ROTO = total)
winner_total <- winners %>% group_by(Manager) %>% summarise(Weeks_Won = n()) %>% arrange(desc(Weeks_Won))

names(winner_total)[2] <- "Weeks Won"


summed_weekly_roto <- all_week_stats %>%
  group_by(real_name,week) %>%
  summarise(total = sum(roto_points)) %>%
  group_by(real_name) %>% 
  summarise(total = sum(total)) %>%
  arrange(desc(total))

names(summed_weekly_roto)[1] <- "Manager"
```
The results only take stats from week 1 to week 21.  Weeks 22, 23, and 24 omitted because those were the playoff weeks, some teams were not paying attention for those weeks. 

# Total Weeks Won
This Table shows how many weeks each team one through out the season
```{r,echo=FALSE}
winner_total %>% 
  kable("html") %>%
  kable_styling(full_width = FALSE)
```

# Weekly ROTO Winners
Here are the winners of each week with their corresponding ROTO score for that week. 

```{r,echo=FALSE}
winners %>% 
  kable("html") %>%
  kable_styling(full_width = FALSE)


```

# Summed weekly ROTO scores

This scoreboard shows the standings if you add up the ROTO points from each team every week.  I found this interseting becuase Noah's team never had the most ROTO points for a single week. But tied for total ROTO over the season.  
```{r,echo=FALSE}
summed_weekly_roto %>% 
  kable("html",row.names = TRUE) %>%
  kable_styling(full_width = FALSE)
```
