---
title: "Weekly Stats"
output: 
  html_document:
    toc: false
---

These are the stats from every team each week. With a Roto column added to show how roto points each team recieved. 

```{r, echo=FALSE,message=FALSE,warning=FALSE}
library(tidyverse)
library(DT)
all_week_stats <- read_delim("/Users/noahknoblauch/Baseball/all_week_stats.txt",delim="\t")
```

```{r echo=FALSE}
regular_season_stats <-all_week_stats%>%
  filter(week !=22,week!=23,week!=24)

Scoreboard <- regular_season_stats%>%
  group_by(real_name,week)%>%
  summarise(ROTO=sum(roto_points))%>%
  arrange(week)

winners <- Scoreboard %>%
  group_by(week)%>%
  filter(ROTO==max(ROTO))
  
winner_total <- winners%>%
  group_by(real_name)%>% summarise(weeks_won = n())%>% arrange(desc(weeks_won))
  
week_value<-list()

for (i in 1:21){
  week<- all_week_stats%>% filter(week==i)%>%select(real_name,stats,stat_value)
  df <- spread(week,stats,stat_value)

  week_roto <-Scoreboard %>%filter(week==i)%>%select(ROTO,real_name)
  week_stats <- inner_join(df,week_roto,by="real_name")
  week_value[[i]] <-week_stats
}



```


```{r,echo=FALSE}
datatable(week_value[[1]], caption = "Week 1 Stats")

```

# Week2

```{r}
datatable(week_value[[2]], caption = "Week 2 Stats")
```


datatable(week_value[[3]], caption = "Week 3 Stats")
datatable(week_value[[4]], caption = "Week 4 Stats")
datatable(week_value[[5]], caption = "Week 5 Stats")
datatable(week_value[[6]], caption = "Week 6 Stats")
datatable(week_value[[7]], caption = "Week 7 Stats")
datatable(week_value[[8]], caption = "Week 8 Stats")
datatable(week_value[[9]], caption = "Week 9 Stats")
datatable(week_value[[10]], caption = "Week 10 Stats")
datatable(week_value[[11]], caption = "Week 11 Stats")
datatable(week_value[[12]], caption = "Week 12 Stats")
datatable(week_value[[13]], caption = "Week 13 Stats")
datatable(week_value[[14]], caption = "Week 14 Stats")
datatable(week_value[[15]], caption = "Week 15 Stats")
datatable(week_value[[16]], caption = "Week 16 Stats")
datatable(week_value[[17]], caption = "Week 17 Stats")
datatable(week_value[[18]], caption = "Week 18 Stats")
datatable(week_value[[19]], caption = "Week 19 Stats")
datatable(week_value[[20]], caption = "Week 20 Stats")
datatable(week_value[[21]], caption = "Week 21 Stats")


```



